---
title: "Template for ITS lectures"
author: "Author name"
date: "`r Sys.Date()` Week 17. For TRAN5015."
output: 
  ioslides_presentation: 
    self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Context: Sustainable Spatial Planning and Analysis

- From AAARRRRGGGGGH to R Getting your hands dirty with data
- Practical calculating accessibility measures in R and QGIS and visualising the results

Requirements: students are recommended to have the latest versions of R, RStudio and QGIS installed on their computers.

Learning outcomes: students will learn how to download and visualise spatial data with R

## Datasets

- Reproducible approach will be used, starting from the data
- OpenStreetMap data on roads: Dutch Road Network data for Groningen: http://download.geofabrik.de/europe.html
- Census OD data on movement patterns: http://wicid.ukdataservice.ac.uk/

## Illustrative work

```{r, echo=TRUE}
library(tmap)
b = bb("Groningen")
r = read_osm(b, type = "opencyclemap")
tm_shape(r) +
  tm_raster(r)
```


