---
title: "Recap on R for SSPA"
author: "Robin Lovelace "
date: "SSPA course`r Sys.Date()`. Code: https://github.com/ITSLeeds/SSPA"
output:
  ioslides_presentation:
    transition: slower
logo: ../figures/its-logo-square.png
bibliography: ../references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Recap: why R?

- Reproducibility requires operations to be encoded in computer code
- That is why a command line interface (CLI) is so powerful
- Solutions are more sustainable if they can be reproduced

Requirements: students are recommended to have the latest versions of R, RStudio and QGIS installed on their computers.

## Recap: accessing data in R

Data can be accessed from a number of places including

- OpenStreetMap via the **osmdata** package and the **overpass** website: http://overpass-turbo.eu/ - see here for parks stops in Leeds for example: http://overpass-turbo.eu/s/xWZ (global)

- The Propensity to Cycle Tool [@lovelace_propensity_2017] (Lovelace et al. 2107), which allows you to download census data on desire lines and routes in the "Region data tab", e.g for West Yorkshire (national): http://www.pct.bike/m/?r=west-yorkshire

- Search online and read-in data with functions such as `read.csv()` and `read_csv()` using the **tidyverse** package (worldwide)

## Reading data

We'll use the **sf** package to read the data.

To install the package, use the following command:

```{r, eval=FALSE}
install.packages("sf")
```

See [@lovelace_geocomputation_2018] for more info


## Reading data II

To make the functions available from the package we've just installed, use the `library` function, as follows:

```{r}
library(sf)
```

Now we can use the new powers enabled by this package, like reading in a shapefile:

```{r}
stns = st_read("~/ITSLeeds/SSPA/data/stations UK/station_point.shp")
```

## Further resources

- The RStudio Cheatsheet: https://www.rstudio.com/wp-content/uploads/2016/01/rstudio-IDE-cheatsheet.pdf
- stplanr tutorials:
    - https://cran.r-project.org/web/packages/stplanr/vignettes/introducing-stplanr.html
    - https://cran.r-project.org/web/packages/stplanr/vignettes/stplanr-paper.html
- Efficient R Programming book: https://csgillespie.github.io/efficientR/
- [Creating Maps With R](https://github.com/Robinlovelace/Creating-maps-in-R) is a good resource for basic mapping in R, using the **sp** package

## References
